Particle-in-cell simulation of ion and electron acceleration in trans-relativistic shocks.

### 2017-11-10 papers/Physica2017/Romansky_Physica2017.tex
left fourier
abstract

\begin{document}
\title{Particle-in-cell simulation of shock waves with different kinds of ions.}

\author{V I Romanky$^{1,2}$, A M Bykov$^1$, S M Osipov$^1$ and P E Gladilin$^1$}

@@

\begin{abstract}
The problem of Cosmic Ray (CR) origin and acceleration is a widely discussed problem of
modern astrophysics. It is considered that most likely CR sources are supernova remnant
shock waves. One of the methods to study particle injection and acceleration by shock
waves is a particle-in-cell computer simulation. In this paper we present results of shock
wave simulations based on our self-developed implicit particle-in-cell code. First, we test the code
with the well-known two stream and Weibel instabilities and second, simulate shock waves in
plasma with different particle composition. Using the obtained results we study the
process of charged particle acceleration at the shock front.
\end{abstract}
\input{intro.tex}
\input{model.tex}
\input{test.tex}
\input{shock.tex}
\input{conclusions.tex}
\input{biblio.tex}
\end{document}

>>>>

\begin{document}
\title{Particle-in-cell simulation of ion and electron acceleration in trans-relativistic shocks.}

\author{V I Romansky$^{1,2}$, A M Bykov$^1$, S M Osipov$^1$ and P E Gladilin$^1$}

@@

\begin{abstract}
The problem of Cosmic Ray (CR) origin and acceleration is a widely discussed problem of
modern astrophysics. It is considered that most likely CR sources are supernova remnant
shock waves. One of the methods to study particle injection and acceleration by shock
waves is a particle-in-cell computer simulation. In this paper we present results of shock
wave simulations based on our self-developed implicit particle-in-cell code. 
\end{abstract}
\input{intro.tex}
\input{model.tex}
\input{test.tex}
\input{shock.tex}
\input{conclusions.tex}
\input{biblio.tex}
\end{document}
